Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
update Table 4 for model-predicted image positions

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Radio observation and model-predicted lensed image positions.}
  \begin{tabular}{@{}ccccc}

@@

Component	&\multicolumn{2}{c}{MERLIN}		 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&			\\
					 &East &North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$   \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
\hline
\end{tabular}

%\end{minipage}
\medskip
Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec. Both SIE+expdisk and 2-SIE lens models predict the same lens image positions.

>>>>

\begin{table*}
%\centering
 \begin{minipage}{140mm}
  \caption{Radio observation and model-predicted lensed image positions.}
  \begin{tabular}{@{}ccccccc}

@@

Component	&\multicolumn{2}{c}{MERLIN}		 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$  & $-0.1618$    &  $+0.3680$ \\  
\hline
\end{tabular}

\end{minipage}
\medskip

Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec. Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.

\end{table*}
